---
title: 'Acid paper analysis'
author: "Lorenzo Cappello"
output:
  html_document:
    df_print: paged
---

Tidyverse Packages:
- dplyr (Data manipulation)
- ggplot2 (Plotting)
- tibble (Reimagined Data frames)
- tidyr ("Tidy" data)
- purrr (Functional Programming)
- readr (Reading data)
- stringr (Strings)
- forcats (Factors)

and a few more... I'll mainly cover `dplyr`, which has the data manipulation functions.  The most influential ones are `dplyr` and `ggplot2`.


Most of the following is adapted from the `dplyr` tutorial [here](https://genomicsclass.github.io/book/pages/dplyr_tutorial.html), by Rafael Irizarry and Michael Love.


```{r}
if(!"tidyverse" %in% installed.packages()) install.packages("tidyverse")
library(tidyverse)
library(dplyr)
```

We first import data to play with:
"summary_varcp_11-2.rda" is the one for the paper Table 1

```{r}

#My guess is that he paper is based on summary_varcp_3-23-23.rda
load("run1/summary_acid.rda")
d <- a$d

d[,4:7] <- d %>% select(env:dev) %>% mutate_if(is.factor,as.character) %>% mutate_if(is.character,as.numeric)

head(d)
summary(d)
```
Looks like there are some awful runs
```{r}
idx <- which(d$rwd>10^10)
head(d[idx,])
#at least I remove this data =36 for now
d <- d %>% filter(data != 36)
```

```{r eval=FALSE}


table(d$method)
```


`dplyr` is (mostly) easier to work with, as compared to base R for data manipulation.  

Important `dplyr` verbs to remember:
*  `select()`:    select columns
*  `filter()`:    filter rows
*  `arrange()`:   re-order / arrange rows
*  `mutate()`:    create new columns
*  `summarise()`: summarise values
*  `group_by()`:  allows for group operations in the "split-apply-combine" concept




Start doing some checks on the first two measures

```{r}

r1 <- d %>% select(method,env,dev,rwd,bias,n) %>% group_by(n,method) %>% summarise_all(.funs = c(sum="mean"))
r1
```
```{r}
ggplot(d, aes(x = method, y = env)) +
  geom_violin(trim = FALSE) +  # Violin plot
  geom_jitter(width = 0.2, color = "blue", alpha = 0.6) +  # Jittered points
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, alpha = 0.3) +  facet_wrap(~n) + # Boxplot
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

```


```{r,warning=FALSE}
r <-d %>% select(method,env,dev,rwd,bias,n) %>% group_by(method,n) %>% summarise_all(.funs = c(med="median"))
r
```




Summary

```{r}
sum <- r %>% left_join(r1)
#sum <- sum[order(sum$data,sum$T),]
head(sum)

```


sum  %>% ggplot(aes(x=method,y=abs(avg_err)))+geom_bar(stat="identity")+facet_wrap(.~datatype)+ theme(axis.text.x = element_text(angle = 90))+ylim(0,15)

Filter rows that starts with a given character filter(str_detect(datatype, "^block"))

if you want to end wit ha 
Start working some plots subsetyting the type of dataset 
```{r}
type <-1

 
#sum  %>% ggplot(aes(x=method,y=dev_med))+geom_bar(stat="identity")+ theme(axis.text.x = element_text(angle = 90))

# Convert data to long format
sum_long <- sum %>% filter(n==50) %>%
  pivot_longer(cols = c(dev_med, rwd_med, bias_med, env_med), 
               names_to = "measure", 
               values_to = "value")

# Create faceted bar plot
ggplot(sum_long, aes(x = method, y = value)) +
  geom_bar(stat = "identity") +
  facet_wrap(~measure, scales = "free_y") +  # Separate panels for each measure
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```
Table studying coverage 


```{r}
type <-"prisca"
 
table <- sum  %>% filter(data=="2")  %>% filter(str_detect(method, type)) %>%  select(T,method,avg.cov.9,
,avg.cond.cov.9, avg.cov.inter.9,avg.new.cond.cov.9)

```
Compare epsilon convergence

```{r}
tableeps <- sum %>% filter(data=="1") %>% filter (method %in% c("prisca-eps-0.001-nodelta","prisca-eps-0.1-nodelta","prisca-trueL-eps-0.1-nodelta", "prisca-trueL-eps-0.001","autoprisca-eps-0.001nodelta","autoprisca-eps-0.1nodelta")) %>% select (T,method,avg_err,avg.haus.dir2,avg.time,avg.length,avg.cond.cov.9)

tableeps <- tableeps[,-1]
tableeps[,3:7] <- round(tableeps[,3:7], 2)
#tablebottle <- tablebottle[,-12]
#tablebottle[,11] <- -tablebottle[,11]
head(tableeps)
```



Compare mcp methods 

```{r}
tablemcp <- sum %>% filter(data=="1") %>% filter (grepl('mcp', method)) %>% select (T,method,avg_err,avg.haus.dir2,avg.time,avg.length,avg.cond.cov.9)

tablemcp <- tablemcp[,-1]
tablemcp[,3:7] <- round(tablemcp[,3:7], 2)
#tablebottle <- tablebottle[,-12]
#tablebottle[,11] <- -tablebottle[,11]
head(tablemcp)
```

Now, let's reduce the table and prepare the tables
This one is for the main text
Debatable choice
```{r}
tablebottle <- sum %>% filter(data=="1") %>% filter (method %in% c("prisca-eps-0.1-nodelta", "prisca-trueL-eps-0.1-nodelta","autoprisca-eps-0.1nodelta", "pelt","binSeg","segNeigh","mcp-iter2000","mcp-iter3000","mcp-iter4000")) %>% select (T,method,avg_err,avg.haus.dir2,avg.time,avg.length,avg.cov.inter.9)

#tablebottle <- tablebottle[,-1]
tablebottle <- tablebottle[-c(2,10),]
tablebottle$method <- as.character(tablebottle$method)
tablebottle$method[tablebottle$method=="prisca-trueL-eps-0.1-nodelta"] <- "ora-PRISCA"
tablebottle$method[tablebottle$method=="autoprisca-eps-0.1nodelta"] <- "auto-PRISCA"
tablebottle$method[tablebottle$method=="prisca-eps-0.1-nodelta"] <- "PRISCA"
tablebottle$method[tablebottle$method=="pelt"] <- "PELT"
tablebottle$method[tablebottle$method=="binSeg"] <- "BINSEG"
tablebottle$method[tablebottle$method=="segNeigh"] <- "SEGNEI"
tablebottle$method[tablebottle$method=="mcp-iter2000"] <- "MCP"
tablebottle$method[tablebottle$method=="mcp-iter3000"] <- "MCP"
tablebottle$method[tablebottle$method=="mcp-iter4000"] <- "MCP"
tablebottle[,3:7] <- round(tablebottle[,3:7], 2)
#tablebottle <- tablebottle[,-12]
#tablebottle[,11] <- -tablebottle[,11]
head(tablebottle)
```


Print these for the latex 
```{r}
library(stargazer)
tablebottle$T <- as.character(tablebottle$T)
tablebottle$method <- as.character(tablebottle$method)
colnames(tablebottle) <- c( "T","method", "error" ,"haus","avg.time", "length" ,"conditional cov")
stargazer(tablebottle, summary=FALSE, rownames=FALSE)

```
